---
title: "Peer2"
author: "Fideborios"
date: "Friday, February 20, 2015"
output: html_document
---

First of all we are loading the necessary library 'Knitr'

```{r,eval=FALSE,message=FALSE}
library(knitr)

```

Second step is loading the data
```{r}
data(mtcars)
```
Lets take a look
```{r}
head(mtcars)

levels(mtcars$am)= c("Auto", "Manual")

```


Our concern is if automatic transmission consumps more fuel than manual or the opposite.

```{r, echo=FALSE}
boxplot(mpg ~ am,
      range= 50,
      data = mtcars, 
      main = "Mpg by transmission type", 
      xlab = "Transmission type",
      ylab = "Miles per gallon")
```

##### As we can see in the above Boxplot the manual transmission consumes fewer fuel

Lets observe the statistical difference.
A good way to compare 2 means is the t-test
```{r}
with(mtcars, t.test(mpg[am == 0], mpg[am == 1]))
```
###### The means of mpg is 17.14737 for manual and 24.39231 for automatic transmissions. The differnce = -3.7671 that leads to p-value = 0.001374 indicating statistical significance to 95% level of significance.

Next step is to have a linear model with the am variable only
```{r, echo=FALSE}
lm(mpg ~ am ,data=mtcars)
```

Now we can interpret our results the automatic transmission cars travel  7.245 miles per galon more than the manual transmission cars.

```{r, echo=FALSE}
lm(mpg ~ cyl + disp+ hp+ drat +wt +qsec +am +gear +carb ,data=mtcars)
```
When we insert all the variables we observe that the coefficient lowers. This means that there are highly correlated other variables that can explain the variability of the mpg

```{r}
cor(mtcars[1:8],mtcars$am, use = "everything",
    method = "spearman")
```
As we can see there are many high correlations.

Using a Stepwise Regression
```{r, results='hide'}
model.all = lm(mpg ~ ., data = mtcars)
n = nrow(mtcars)

model = step(model.all, 
             direction ="both",  # other choices "both" , "forward" # 
             k = log(n) ) #(AIC = - 2*log L + k*df) if k=2 AIC, if k=log(n) BIC#  

```

We find the best fitting model.

```{r}
summary(model)
```

We can write it as : 
######MPG= 9.6178 -3.9165*wt +  1.2259*qsec + 2.9358*am

Now the interpretation is that the automatic transimissioned cars travel 2.9358 more miles per galon than the manual.

Finally we check the fitness of the model
```{r}
mean(model$residuals)
```
the mean of the reiduals is almost equal to zero and seem to be randomly distributed
```{r}
plot(resid(model))
abline(0,0)
```

